---
title: "TexasSTAR_analysis"
author: "Daniel Brock"
date: "2024-08-04"
output: html_document
---

# 0. Setup

```{r setup, include=FALSE}
# Importing requiring Packages
library(plyr)
library(tidyverse)
library(readxl)
library(writexl)
library(finalfit)
library(chisq.posthoc.test)
library(rstatix)
library(emmeans)
library(performance)
library(ggeffects)
library(gtsummary)
library(flextable)
library(RColorBrewer)
library(car)
library(ggpubr)
library(scales)
library(patchwork)
library(DHARMa)
library(MASS)

# Setting the working director
cwd <- getwd()
setwd(cwd)
```



# 1. Importing datasets

```{r}
# Applicant-level information
df <- read.csv(file = "data/STAR_Responses_2017_2023.csv", na.strings = "N/A")
df$degrees <- paste0(df$Degree, "-", df$Other.Degrees)
df$degrees <- plyr::mapvalues(x = df$degrees, from = c("DO-", "MD-"), to = c("DO", "MD"))

# Programs applied to and interviewed at per applicant
programs <- read.csv(file = "data/STAR_Programs_2017_2023.csv")
```



# 2. Data wrangling

```{r}
df_clean <- df %>% mutate(
  
  # Making specialty a factor
  Specialty = Specialty %>% 
    factor(levels = sort(unique(Specialty))),
  
  # Making public schools a factor
  Public_School = Public_School %>% 
    factor(levels = c("No", "Yes")),
  
  # Making Ivy status a factor
  IvyP = IvyP %>% 
    factor(levels = c("No", "Yes")) %>% 
    ff_label("Ivy League"),
  
  # Making match status a factor
  Matched = Matched %>% 
    plyr::mapvalues(from = c("N", "Y"), to = c("No", "Yes")) %>% 
    factor(levels = c("No", "Yes")), 

  # Making home state a factor
  Home.State = Home.State %>% 
    factor(levels = sort(unique(Home.State))),
  
  # Making home region a factor
  Home.Region = Home.Region %>% 
    plyr::mapvalues(from = "", to = NA) %>% 
    plyr::mapvalues(from = c("CGSA", "NEGSA", "SGSA", "WGSA"), to = c("Central", "Northeast", "South", "West")) %>% 
    factor(levels = c("Northeast", "Central", "South", "West")),
    
  # Making step1 ranges a factor
  Step.1 = Step.1 %>% 
    factor(levels = c("190-194", "195-199", "200-204", "205-209", "210-214", "215-219", "220-224", "225-229", "230-234", "235-239", "240-244", "245-249", "250-254", "255-259", "260-264", "265-269", "270 or higher")) %>% 
    ff_label("Step 1 Score"),
  
  # Making step2 ranges a factor
  Step.2.CK = Step.2.CK %>% 
    factor(levels = c("200-204", "205-209", "210-214", "215-219", "220-224", "225-229", "230-234", "235-239", "240-244", "245-249", "250-254", "255-259", "260-264", "265-269", "270 or higher")) %>% 
    ff_label("Step 2 Score"),
  
  # Binning STEP2 CK Release Dates
  Release...Step.2.CK = Release...Step.2.CK %>% plyr::mapvalues(from = "", to = NA),
  Step.2.CK.release = 
    dplyr::case_when(
      Release...Step.2.CK %in% c("Mid September", "Late September", "Early October", "Mid October") ~ "Early",
      Release...Step.2.CK %in% c("Late October", "Early November", "Mid November") ~ "Mid",
      Release...Step.2.CK %in% c("Late November", "Early December", "Mid December", "Late December", "Early January", "Mid January", "Late January", "After Rank List Submission") ~ "Late"
    ) %>% factor(levels = c("Early", "Mid", "Late")),
  
  # Changing Cumulative Quartile into integers
  Cumulative.Quartile = Cumulative.Quartile %>% 
    plyr::mapvalues(from = c("1st", "2nd", "3rd", "4th"), to = c(1, 2, 3, 4)),
  
  # Making honors a factor
  Honors.A.This.Specialty = Honors.A.This.Specialty %>% 
    plyr::mapvalues(from = "", to = NA) %>% 
    factor(levels = c("No", "Yes")) %>% 
    ff_label("Honors in Specialty of Choice"),
  
  # Making AOA status a factor
  AOA.Sigma = AOA.Sigma %>% 
    factor(levels = c("No", "Yes", "No School Chapter")) %>% 
    ff_label("AOA"),
  
  # Making gold humanism a factor
  GHHS = GHHS %>% 
    factor(levels = c("No", "Yes", "No School Chapter")) %>% 
    ff_label("Gold Humanism Honors Society"),
  
  # Making couples matching a factor
  Couples.Match = Couples.Match %>% 
    factor(levels = c("No", "Yes")),
  
  # Making degree a factor - save for later...
  
  # Making taking a research year a factor
  Research.Year = Research.Year %>% 
    factor(levels = c("No", "Yes")),
  
  # Making taking a leave of absence year a factor
  Absence.Year = Absence.Year %>% 
    factor(levels = c("No", "Yes")),
  
  # Making required to remediate a factor
  Required.to.Remediate = Required.to.Remediate %>% 
    factor(levels = c("No", "Yes")),
  
  # Making pass attempt for step1 a factor 
  Pass.Attempt...Step.1 = Pass.Attempt...Step.1 %>% 
    plyr::mapvalues(from = c(""), to = c(NA)) %>% 
    factor(levels = c("1st", "2nd", "3rd")) %>% 
    ff_label("Step1 Pass Attempt"),
  
  # Making pass attempt for step2ck a factor 
  Pass.Attempt...Step.1 = Pass.Attempt...Step.2.CK %>% 
    plyr::mapvalues(from = c(""), to = c(NA)) %>% 
    factor(levels = c("1st", "2nd", "3rd")) %>% 
    ff_label("Step2CK Pass Attempt"),
  
  # Making pass attempt for step2cs a factor 
  Pass.Attempt...Step.1 = Pass.Attempt...Step.2.CS %>% 
    plyr::mapvalues(from = c(""), to = c(NA)) %>% 
    factor(levels = c("1st", "2nd", "3rd")) %>% 
    ff_label("Step2CS Pass Attempt"),
  
  # Making the majority of interview offers a factor
  Majority.of.Interview.Offers = Majority.of.Interview.Offers %>% 
    factor(levels = c("Late September (before MSPE release)", "Promptly after Oct 1 (MSPE release)", "Early October", "Mid October", "Late October", "Early November", "Mid November", "Late November", "Early December", "Mid December")),
  
  # Making the majority of interviews attended a factor
  Majority.of.Interviews.Attended = Majority.of.Interviews.Attended %>% 
    factor(levels = c("October", "November", "December", "January", "February")),
  
  # Making interview cost a factor
  Interview.Cost = Interview.Cost %>% 
    plyr::mapvalues(from = 
                      c("< $500", "<$500", "$500-$999", "$1000-$1499", "$1500-$1999", "$2000-$2499", "$2500-$2999", "$3000-$3499", "$3500-$3999", "$4000-$4499", "$4500-$4999", "$5000-$5499", "$5500-$5999", "$6000-$6499", "$6500-$6999", "$7000-$7499", "$7500-$7999", "$8000-$8499", "$8500-$8999", "$9000-$9499", "$9500-$9999", "$10000-$10499", "$10500-$10999", "$11000-$11499", "$11500-$11599", "$12000 and above"), 
                    to = 
                      c("<$1000", "<$1000", "<$1000", "$1000-$1999", "$1000-$1999", "$2000-$2999", "$2000-$2999", "$3000-$3999", "$3000-$3999", "$4000-$4999", "$4000-$4999", "$5000-$5999", "$5000-$5999", "$6000-$6999", "$6000-$6999", "$7000-$7999", "$7000-$7999", "$8000-$8999", "$8000-$8999", "$9000-$9999", "$9000-$9999", "$10000-$10999", "$10000-$10999", "$11000-$11999", "$11000-$11999", ">$12000")) %>% 
    factor(levels = c("<$1000", "$1000-$1999", "$2000-$2999", "$3000-$3999", "$4000-$4999", "$5000-$5999", "$6000-$6999", "$7000-$7999", "$8000-$8999", "$9000-$9999", "$10000-$10999", "$11000-$11999", ">$12000")),
  
  # Making Application fees a factor
  Application.Fees = Application.Fees %>% 
    plyr::mapvalues(from = c("$3500 and above"), to = c(">$3500")) %>% 
    factor(levels = c("<$500", "$500-$999", "$1000-$1499", "$1500-$1999", "$2000-$2499", "$2500-$2999", "$3000-$3499", ">$3500")),
  
  # Making virtual interview costs a factor
  Virtual.Interview.Cost = Virtual.Interview.Cost %>% 
    plyr::mapvalues(from = c("< $50", "> $300"), to = c("<$50", ">$300")) %>% 
    factor(levels = c("<$50", "$50-$100", "$101-$150", "$151-$200", "$201-$250", "$251-$300", ">$300")),
  
  # Making other costs a factor
  Other.Costs = Other.Costs %>% 
    plyr::mapvalues(from = 
                      c("< $500", "<$500", "$500-$999", "$1000-$1499", "$1500-$1999", "$2000-$2499", "$2500-$2999", "$3000-$3499", "$3500-$3999", "$4000-$4499", "$4500-$4999", "$5000-$5499", "$5500-$5999", "$6000-$6499", "$6500-$6999", "$7000-$7499", "$7500-$7999", "$8000-$8499", "$8500-$8999", "$9000-$9499", "$9500-$9999", "$10000 and above"), 
                    to = 
                      c("<$1000", "<$1000", "<$1000", "$1000-$1999", "$1000-$1999", "$2000-$2999", "$2000-$2999", "$3000-$3999", "$3000-$3999", "$4000-$4999", "$4000-$4999", "$5000-$5999", "$5000-$5999", "$6000-$6999", "$6000-$6999", "$7000-$7999", "$7000-$7999", "$8000-$8999", "$8000-$8999", "$9000-$9999", "$9000-$9999",  ">$10000")) %>% 
    factor(levels = c("<$1000", "$1000-$1999", "$2000-$2999", "$3000-$3999", "$4000-$4999", "$5000-$5999", "$6000-$6999", "$7000-$7999", "$8000-$8999", "$9000-$9999", ">$10000")),
  
  # Making Total costs a factor
  Total.Costs = Total.Costs %>% 
    plyr::mapvalues(from = 
                      c("< $500", "<$500", "$500-$999", "$1000-$1499", "$1500-$1999", "$2000-$2499", "$2500-$2999", "$3000-$3499", "$3500-$3999", "$4000-$4499", "$4500-$4999", "$5000-$5499", "$5500-$5999", "$6000-$6499", "$6500-$6999", "$7000-$7499", "$7500-$7999", "$8000-$8499", "$8500-$8999", "$9000-$9499", "$9500-$9999", "$10000-$10499", "$10500-$10999", "$11000-$11499", "$11500-$11999", "$12000-$12499", "$12500-$12999", "$13000-$13499", "$13500-$13999", "$14000-$14499", "$14500-$14999", "$15000-$15499", "$15500-$15999", "$16000-$16499", "$16500-$16999", "$17000-$17499", "$17500-$17999", "$18000-$18499", "$18500-$18999", "$19000-$19499", "$19500-$19999", "$20000-$20499", "$20500-$20999", "$21000-$21499", "$21500-$21999", "$22000-$22499", "$22500-$22999", "$23000-$23499", "$23500-$23999", "$24000-$24499", "$24500-$24999", "$25000 and above"),
                    to = 
                      c("<$1000", "<$1000", "<$1000", "$1000-$1999", "$1000-$1999", "$2000-$2999", "$2000-$2999", "$3000-$3999", "$3000-$3999", "$4000-$4999", "$4000-$4999", "$5000-$5999", "$5000-$5999", "$6000-$6999", "$6000-$6999", "$7000-$7999", "$7000-$7999", "$8000-$8999", "$8000-$8999", "$9000-$9999", "$9000-$9999", "$10000-$10999", "$10000-$10999", "$11000-$11999", "$11000-$11999", "$12000-$12999", "$12000-$12999", "$13000-$13999", "$13000-$13999", "$14000-$14999", "$14000-$14999", "$15000-$15999", "$15000-$15999", "$16000-$16999", "$16000-$16999", "$17000-$17999", "$17000-$17999", "$18000-$18999", "$18000-$18999", "$19000-$19999", "$19000-$19999", "$20000-$20999", "$20000-$20999", "$21000-$21999", "$21000-$21999", "$22000-$22999", "$22000-$22999", "$23000-$23999", "$23000-$23999", "$24000-$24999", "$24000-$24999", ">$25000")) %>% 
    factor(levels = c("<$1000", "$1000-$1999", "$2000-$2999", "$3000-$3999", "$4000-$4999", "$5000-$5999", "$6000-$6999", "$7000-$7999", "$8000-$8999", "$9000-$9999", "$10000-$10999", "$11000-$11999", "$12000-$12999", "$13000-$13999", "$14000-$14999", "$15000-$15999", "$16000-$16999", "$17000-$17999", "$18000-$18999", "$19000-$19999", "$20000-$20999", "$21000-$21999", "$22000-$22999", "$23000-$23999", "$24000-$24999", ">$25000")),
  
  # Making Virtual Environment a factor 
  Virtual.Environment = Virtual.Environment %>% 
    factor(levels = c("Strongly Agree", "Agree", "Undecided", "Disagree", "Strongly Disagree")),
  
  # Making ERAS supplemental a factor 
  ERAS.Supplemental = ERAS.Supplemental %>% 
    factor(levels = c("Strongly Agree", "Agree", "Undecided", "Disagree", "Strongly Disagree")),
  
  # Making Demographic Willingness a factor
  Demographic.Willingness = Demographic.Willingness %>% 
    plyr::mapvalues(from = c("N", "Y"), to = c("No", "Yes")) %>% 
    factor(levels = c("No", "Yes")),
  
  # Making age group a factor
  Age.Group = Age.Group %>% 
    plyr::mapvalues(from = c("< 25", ">39"), to = c("<25", ">40")) %>% 
    factor(levels = c("<25", "25-27", "28-30", "31-33", "34-36", "37-39", ">40")),
  
  # making sexual orientation a factor
  Sexual.Orientation = Sexual.Orientation %>% 
    factor(levels = c("Male", "Female", "Intersex", "Prefer not to answer")) %>% 
    ff_label("Gender"),
  
  # Making race/ethncity a factor
  Race.Ethnicity = Race.Ethnicity %>% 
    plyr::mapvalues(from = c("N", "Y"), to = c("No", "Yes")) %>% 
    factor(levels = c("No", "Yes")) %>% 
    ff_label("Underrepresented in Medicine"),
  
  # Making first generation college a factor
  First.Generation.College = First.Generation.College %>% 
    plyr::mapvalues(from = c("N", "Y"), to = c("No", "Yes")) %>% 
    factor(levels = c("No", "Yes")),
  
  # Making food & housing insecurity a factor
  Food.Housing.Insecurity = Food.Housing.Insecurity %>% 
    plyr::mapvalues(from = c("N", "Y"), to = c("No", "Yes")) %>% 
    factor(levels = c("No", "Yes"))
)
```



# 3. Demographics

## 3.1 Table 1 basic demographic statistics

```{r}
# Dependent and explanatory variables
dependent = "degrees"
explanatory = c("Specialty", "Public_School", "IvyP", "Applied_Total", "InterviewOffer_Total", "Matched", "Step.1", "Step.2.CK", "Cumulative.Quartile", "Quartile.Rank", "X..Honored.Clerkships", "Honors.A.This.Specialty", "AOA.Sigma", "GHHS", "Couples.Match", "X..Research.Experiences", "X..Abstracts..Pres..Posters", "X..Peer.Rev.Publications", "X..Volunteer.Experiences", "X..Leadership.Positions", "Required.to.Remediate", "Pass.Attempt...Step.1", "Pass.Attempt...Step.2.CK", "Pass.Attempt...Step.2.CS", "Majority.of.Interview.Offers", "Majority.of.Interviews.Attended", "X..Interviews.Attended", "Interview.Cost", "Application.Fees", "Virtual.Interview.Cost", "Other.Costs", "Virtual.Environment", "ERAS.Supplemental", "Demographic.Willingness", "Age.Group", "Sexual.Orientation", "Race.Ethnicity", "First.Generation.College", "Food.Housing.Insecurity")

table1 <- df_clean[df_clean$degrees %in% c("MD", "MD-MPH", "MD-PhD"), ]  #filtering for MD students whose group > 1000 for now

table1 <- table1 %>% 
  summary_factorlist(
    dependent = dependent, explanatory = explanatory,
    add_col_totals = TRUE, include_col_totals_percent = TRUE, p = TRUE, cont = "median",
    p_cat = "chisq"
    #cont = "median", p = TRUE, p_cat = "chisq", digits = 2, na_include = TRUE, 
  )

# Optional export to excel
#write_xlsx(table1, path = paste0(cwd, "/tables/table1.xlsx"))
```



## 3.2 Demographic Analysis

```{r}
# Finalfit table for demographic factors
pred_factors <- c("Age.Group", "Sexual.Orientation", "Race.Ethnicity", "Food.Housing.Insecurity", "First.Generation.College", "Home.Region", "Public_School", "IvyP")
dual_degrees <- c("MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")

df_list <- list()
for (predictor in pred_factors) {
  print(predictor)
  demographics_table <- df_clean %>% dplyr::filter(degrees %in% c("MD", dual_degrees)) %>% 
    summary_factorlist(dependent = "degrees", explanatory = c(predictor), 
                       add_col_totals = TRUE, include_col_totals_percent = TRUE, 
                       p = TRUE, cont = "median", p_cat = "chisq")
  demographics_table$demographic <- predictor
  df_list[[predictor]] <- demographics_table
}
demo_df <- dplyr::bind_rows(df_list)

# Exporting to excel
#write_xlsx(x = demo_df, path = "tables/demographics.xlsx")
```

```{r}
# Fisher and pairwise stuff

# Age groups
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(!is.na(Age.Group))
  dt <- table(dt$Age.Group, dt$degrees) %>% as.data.frame.matrix()
  dt <- dt[ , c(2, 1)]
  fisher.test(dt, simulate.p.value = T)
  fisher.posthoc <- row_wise_fisher_test(dt, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "Age"
  df_list[[degree]] <- fisher.posthoc
}
demo_age <- dplyr::bind_rows(df_list)

# Sexual Orientation
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(Sexual.Orientation %in% c("Male", "Female"))
  dt$Sexual.Orientation <- factor(x = dt$Sexual.Orientation, levels = c("Male", "Female"))
  dt <- table(dt$Sexual.Orientation, dt$degrees) %>% as.data.frame.matrix()
  dt2 <- dt[ , c(2, 1)]
  print(degree)
  print(fisher.test(dt, simulate.p.value = T))
  fisher.posthoc <- row_wise_fisher_test(dt2, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "Sex"
  df_list[[degree]] <- fisher.posthoc
}
demo_sex <- dplyr::bind_rows(df_list)

# Race/Ethnicity
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(!is.na(Race.Ethnicity))
  dt <- table(dt$Race.Ethnicity, dt$degrees) %>% as.data.frame.matrix()
  dt2 <- dt[ , c(2, 1)]
  print(degree)
  print(fisher.test(dt, simulate.p.value = T))
  fisher.posthoc <- row_wise_fisher_test(dt2, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "URM Status"
  df_list[[degree]] <- fisher.posthoc
}
demo_urm <- dplyr::bind_rows(df_list)

# Food / Housing Insecurity
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(!is.na(Food.Housing.Insecurity))
  dt <- table(dt$Food.Housing.Insecurity, dt$degrees) %>% as.data.frame.matrix()
  dt2 <- dt[ , c(2, 1)]
  print(degree)
  print(fisher.test(dt, simulate.p.value = T))
  fisher.posthoc <- row_wise_fisher_test(dt2, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "Food/Housing Insecurity"
  df_list[[degree]] <- fisher.posthoc
}
demo_food_housing <- dplyr::bind_rows(df_list)

# First Generation
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(!is.na(First.Generation.College))
  dt <- table(dt$First.Generation.College, dt$degrees) %>% as.data.frame.matrix()
  dt2 <- dt[ , c(2, 1)]
  print(degree)
  print(fisher.test(dt, simulate.p.value = T))
  fisher.posthoc <- row_wise_fisher_test(dt2, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "First Generation"
  df_list[[degree]] <- fisher.posthoc
}
demo_first_gen <- dplyr::bind_rows(df_list)

# Home Region
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(!is.na(Home.Region))
  dt <- table(dt$Home.Region, dt$degrees) %>% as.data.frame.matrix()
  dt <- dt[ , c(2, 1)]
  fisher.test(dt, simulate.p.value = T)
  fisher.posthoc <- row_wise_fisher_test(dt, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "Home Region"
  df_list[[degree]] <- fisher.posthoc
}
demo_home_region <- dplyr::bind_rows(df_list)

# Public School
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(!is.na(Public_School))
  dt <- table(dt$Public_School, dt$degrees) %>% as.data.frame.matrix()
  dt2 <- dt[ , c(2, 1)]
  print(degree)
  print(fisher.test(dt, simulate.p.value = T))
  fisher.posthoc <- row_wise_fisher_test(dt2, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "Public School"
  df_list[[degree]] <- fisher.posthoc
}
demo_public_school <- dplyr::bind_rows(df_list)

# Ivy
df_list <- list()
for (degree in dual_degrees) {
  dt <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree)) %>% dplyr::filter(!is.na(IvyP))
  dt <- table(dt$IvyP, dt$degrees) %>% as.data.frame.matrix()
  dt2 <- dt[ , c(2, 1)]
  print(degree)
  print(fisher.test(dt, simulate.p.value = T))
  fisher.posthoc <- row_wise_fisher_test(dt2, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "Ivy"
  df_list[[degree]] <- fisher.posthoc
}
demo_ivy <- dplyr::bind_rows(df_list)


# Merging all demographic fisher tests into a single dataframe
demo_df_fish <- dplyr::bind_rows(list(demo_age, demo_sex, demo_urm, demo_food_housing, demo_first_gen, demo_home_region, demo_public_school, demo_ivy))

# Exporting to excel
#write_xlsx(x = demo_df_fish, path = "tables/demographics_fisher.xlsx")
```



# 4. Activities and Test Scores

## 4.1 STEP Scores

```{r}
# STEP1 Scores
step1_scores <- c("190-194", "195-199", "200-204", "205-209", "210-214", "215-219", "220-224", "225-229", "230-234", "235-239", "240-244", "245-249", "250-254", "255-259", "260-264", "265-269", "270 or higher")
step1_centered <- c(192, 197, 202, 207, 212, 217, 222, 227, 232, 237, 242, 247, 252, 257, 262, 267, 271)
df_clean$step1_centered <- plyr::mapvalues(x = df_clean$Step.1, from = step1_scores, to = step1_centered) %>% as.integer()

# STEP2 Scores
step2_scores <- c("200-204", "205-209", "210-214", "215-219", "220-224", "225-229", "230-234", "235-239", "240-244", "245-249", "250-254", "255-259", "260-264", "265-269", "270 or higher")
step2_centered <- c(202, 207, 212, 217, 222, 227, 232, 237, 242, 247, 252, 257, 262, 267, 271)
df_clean$step2_centered <- plyr::mapvalues(x = df_clean$Step.2.CK, from = step2_scores, to = step2_centered) %>% as.integer()

# Calculating STEP2 Scores relative to STEP1
df_clean$STEP_relative <- df_clean$step2_centered - df_clean$step1_centered

# Tidying for plotting - STEP1
degree_list <- c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
step1_counts <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% dplyr::filter(!is.na(step1_centered)) %>% 
  dplyr::group_by(degrees, step1_centered) %>% 
  dplyr::summarise(step1_counts = n())
step1_totals <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% dplyr::filter(!is.na(step1_centered)) %>% 
  dplyr::group_by(degrees) %>% 
  dplyr::summarise(step1_totals = n())
step1_counts <- merge(step1_counts, step1_totals, by = "degrees")
step1_counts$step1_centered <- plyr::mapvalues(x = step1_counts$step1_centered, from = 1:17, to = step1_centered) %>% as.integer()
step1_counts$percents <- (step1_counts$step1_counts / step1_counts$step1_totals) * 100

# Tidying for plotting - STEP2
step2_counts <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% dplyr::filter(!is.na(step2_centered)) %>% 
  dplyr::group_by(degrees, step2_centered) %>% 
  dplyr::summarise(step2_counts = n())
step2_totals <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% dplyr::filter(!is.na(step2_centered)) %>% 
  dplyr::group_by(degrees) %>% 
  dplyr::summarise(step2_totals = n())
step2_counts <- merge(step2_counts, step2_totals, by = "degrees")
step2_counts$step2_centered <- plyr::mapvalues(x = step2_counts$step2_centered, from = 1:15, to = step2_centered) %>% as.integer()
step2_counts$percents <- (step2_counts$step2_counts / step2_counts$step2_totals) * 100
```

```{r}
# Plotting for clarity - STEP1
step1_distribution <- step1_counts %>% ggplot(aes(x = step1_centered, y = percents, color = degrees)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "STEP1 Centered Score", y = "Percent of Total (%)", color = "Degrees", title = "STEP1 Score Distribution") +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5))

# Plotting for clarity - STEP2
step2_distribution <- step2_counts %>% ggplot(aes(x = step2_centered, y = percents, color = degrees)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "STEP2 Centered Score", y = "Percent of Total (%)", color = "Degrees", title = "STEP2 Score Distribution") +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5))

# Patchwork to put graphs together
step_distribution <- step1_distribution | step2_distribution
print(step_distribution)

# STEP2 relative to STEP1 score difference
step_delta_plot <- df_clean %>% dplyr::filter(degrees %in% degree_list) %>% 
  ggplot(aes(x = degrees, y = STEP_relative, fill = degrees)) +
  geom_boxplot(outlier.shape = NA) + 
  labs(x = "Degrees", y = "STEP2 Score Delta (STEP2 - STEP1)", fill = "Degrees", title = "STEP2 - STEP1 Score Deltas") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
print(step_delta_plot)

# exporting figures
#ggsave(plot = step_distribution, filename = "figures/step_scores_plot.pdf", width = 4000, height = 1500, dpi = 300, units = "px")
#ggsave(plot = step_delta_plot, filename = "figures/step_delta_plot.pdf", width = 1800, height = 1400, dpi = 300, units = "px")
```

```{r}
# Statistical Tests for STEP1
step1_counts <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% dplyr::filter(!is.na(step1_centered))
step1_counts$step1_centered <- plyr::mapvalues(x = step1_counts$step1_centered, from = 1:17, to = step1_centered)

kruskal_res <- kruskal.test(step1_centered ~ degrees, data = step1_counts)
pairwise_kruskal <- pairwise.wilcox.test(step1_counts$step1_centered, step1_counts$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)

# Statistical Tests for STEP2
step2_counts <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% dplyr::filter(!is.na(step2_centered))
step2_counts$step2_centered <- plyr::mapvalues(x = step2_counts$step2_centered, from = 1:15, to = step2_centered)

kruskal_res <- kruskal.test(step2_centered ~ degrees, data = step2_counts)
pairwise_kruskal <- pairwise.wilcox.test(step2_counts$step2_centered, step2_counts$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)

# Statistical Tests for STEP Delta
step_delta <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% dplyr::filter(!is.na(STEP_relative))

kruskal_res <- kruskal.test(STEP_relative ~ degrees, data = step_delta)
pairwise_kruskal <- pairwise.wilcox.test(step_delta$STEP_relative, step_delta$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)

# Statistical Tests for time of STEP2 CK release
df_list <- list()
dual_degrees <- c("MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
for (degree in dual_degrees) {
  dt <- df_clean %>% 
    dplyr::filter(degrees %in% c("MD", degree)) %>% 
    dplyr::filter(!is.na(Step.2.CK.release))
  dt <- table(dt$Step.2.CK.release, dt$degrees) %>% as.data.frame.matrix()
  dt2 <- dt[ , c(2, 1)]
  print(degree)
  print(fisher.test(dt, simulate.p.value = T))
  fisher.posthoc <- row_wise_fisher_test(dt2, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degree <- degree
  fisher.posthoc$predictor <- "STEP2 Release"
  df_list[[degree]] <- fisher.posthoc
}
demo_step2_release <- dplyr::bind_rows(df_list)
```

```{r}
# Table for STEP1 - median or mean?
step1_table <- step1_counts %>% summary_factorlist(
  dependent = "degrees", explanatory = c("step1_centered"), cont = "mean", p = T, 
  add_col_totals = TRUE, include_col_totals_percent = TRUE
)

# Table for STEP2
step2_table <- step2_counts %>% summary_factorlist(
  dependent = "degrees", explanatory = c("step2_centered"), cont = "mean", p = T, 
  add_col_totals = TRUE, include_col_totals_percent = TRUE
)

# Table for Delta STEP (STEP2 - STEP1)
step_diff_table <- df_clean %>% dplyr::filter(degrees %in% degree_list) %>% 
  summary_factorlist(
    dependent = "degrees", explanatory = c("STEP_relative"), cont = "mean", p = T, 
  add_col_totals = TRUE, include_col_totals_percent = TRUE
)

# Table for STEP2 CK Release data
step2_release_table <- df_clean %>% dplyr::filter(degrees %in% degree_list) %>% 
  summary_factorlist(
    dependent = "degrees", explanatory = c("Step.2.CK.release"), p_cat = "chisq", p = T, 
    add_col_totals = TRUE, include_col_totals_percent = TRUE
  )

# Merging into a STEP table to export
step_table <- dplyr::bind_rows(step1_table, step2_table, step_diff_table, step2_release_table)

# Exporting as excel
#write_xlsx(x = step_table, path = "tables/STEP_metrics.xlsx")
```



## 4.2 Class Quartiles

```{r}
# Function to calculate stats and pairwise comparisons for class quartiles
quartile_calculator <- function(comparison, dual_degree) {
  quartile_df <- df_clean %>% 
    dplyr::filter(degrees %in% c("MD", dual_degree)) %>% 
    dplyr::filter(!is.na(comparison))
  quartile_df <- table(quartile_df$degrees, quartile_df[[comparison]]) %>% as.data.frame.matrix() %>% t()
  quartile_df <- quartile_df[ , c(2, 1)]
  print(quartile_df)
  
  chi_res <- chisq.test(quartile_df)
  print(chi_res)
  chi_posthoc <- chisq.posthoc.test(quartile_df, method = "fdr")
  fisher.posthoc <- row_wise_fisher_test(quartile_df, p.adjust.method = "fdr", detailed = T)
  fisher.posthoc$degrees <- dual_degree
  return(fisher.posthoc)
}
```

```{r}
# Cumulative quartile
quartile_mdphd <- quartile_calculator(comparison = "Cumulative.Quartile", dual_degree = "MD-PhD")
quartile_mdmph <- quartile_calculator(comparison = "Cumulative.Quartile", dual_degree = "MD-MPH")
quartile_mdmba <- quartile_calculator(comparison = "Cumulative.Quartile", dual_degree = "MD-MBA")
quartile_mdmsc <- quartile_calculator(comparison = "Cumulative.Quartile", dual_degree = "MD-MSc")
cumulative_quartile <- dplyr::bind_rows(list(quartile_mdphd, quartile_mdmph, quartile_mdmba, quartile_mdmsc))
cumulative_quartile$quartile_metric <- "Cumulative Quartile"

# Quartile Rank
rankq_mdphd <- quartile_calculator(comparison = "Quartile.Rank", dual_degree = "MD-PhD")
rankq_mdmph <- quartile_calculator(comparison = "Quartile.Rank", dual_degree = "MD-MPH")
rankq_mdmba <- quartile_calculator(comparison = "Quartile.Rank", dual_degree = "MD-MBA")
rankq_mdmsc <- quartile_calculator(comparison = "Quartile.Rank", dual_degree = "MD-MSc")
rank_quartile <- dplyr::bind_rows(list(rankq_mdphd, rankq_mdmph, rankq_mdmba, rankq_mdmsc))
rank_quartile$quartile_metric <- "Quartile Rank"

# Merging
quartile_df <- dplyr::bind_rows(list(cumulative_quartile, rank_quartile))

# Exporting to excel
#write_xlsx(x = quartile_df, path = "tables/quartiles.xlsx")
```



## 4.3 Honors and Experiences

```{r}
honors_function <- function(comparison, plot_title) {
  # Cleaning the data for plotting
  degree_list <- c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
  honors_df <- df_clean %>% 
    dplyr::filter(degrees %in% degree_list) %>%
    dplyr::filter(!is.na(comparison))
  
  # Plotting
  p <- honors_df %>% dplyr::filter(degrees %in% degree_list) %>% 
    ggplot(aes(x = honors_df[[comparison]], fill = degrees)) + 
    geom_histogram(center = 0, binwidth = 1, color = "black") +
    facet_wrap(~degrees, ncol = 5, scales = "free_y") + 
    scale_y_continuous(expand = c(0, 0)) +
    labs(x = plot_title, y = "Counts", title = plot_title) +
    theme_classic() +
    theme(strip.background = element_blank(),
          plot.title = element_text(hjust = 0.5))
  print(p)
  
  # Statistical testing with non-parametric kruskal and post hoc 
  kruskal_res <- kruskal.test(honors_df[[comparison]], honors_df$degrees)
  pairwise_kruskal <- pairwise.wilcox.test(honors_df[[comparison]], honors_df$degrees, p.adjust.method = "fdr")
  print(kruskal_res)
  print(pairwise_kruskal)
  ret_list <- list("plot" = p, "stats" = pairwise_kruskal)
  return(ret_list)
}
```

```{r}
# Plotting and Stats for Number of Research Experiences
research_experiences <- honors_function(comparison = "X..Research.Experiences", plot_title = "Number of Reseach Experiences")

# Plotting and Stats for Number of Abstracts, Presentations, and Posters
abstracts_posters <- honors_function(comparison = "X..Abstracts..Pres..Posters", plot_title = "Number of Abstracts/Presentations/Posters")

# Plotting and Stats for Number of Peer reviewed publications
publications <- honors_function(comparison = "X..Peer.Rev.Publications", plot_title = "Number of Publications")

# Plotting and Stats for Number of Volunteer Experiences
volunteering <- honors_function(comparison = "X..Volunteer.Experiences", plot_title = "Number of Volunteering Experiences")

# Plotting and Stats for Number of Leadership experiences
leadership <- honors_function(comparison = "X..Leadership.Positions", plot_title = "Number of Leadership Positions")

# Plotting and Stats for Number of Honored Clerkships
honors_clerkships <- honors_function(comparison = "X..Honored.Clerkships", plot_title = "Number of Honors in Clerkships")
```

```{r}
# Function to extract stats and format the results of the pairwise wilcox test to a dataframe
stat_extracter <- function(activity_list, activity) {
  df_stats <- activity_list$stats$p.value %>% as.data.frame()
  df_stats <- df_stats %>% tibble::rownames_to_column(var = "degree")
  df_stats$activity <- activity
  return(df_stats)
}

# Exporting Stats
research_experiences_stats <- stat_extracter(activity_list = research_experiences, activity = "number of research experiences")
abstracts_posters_stats <- stat_extracter(activity_list = abstracts_posters, activity = "number of abstracts, presentations, and posters")
publications_stats <- stat_extracter(activity_list = publications, activity = "number of publications")
volunteering_stats <- stat_extracter(activity_list = volunteering, activity = "number of volunteering experiences")
leadership_stats <- stat_extracter(activity_list = leadership, activity = "number of leadership experiences")
honors_clerkships_stats <- stat_extracter(activity_list = honors_clerkships, activity = "number of honors clerkships")

# Merging and exporting to excel
activity_df <- dplyr::bind_rows(list(research_experiences_stats, abstracts_posters_stats, publications_stats, volunteering_stats, leadership_stats, honors_clerkships_stats))
#write_xlsx(x = activity_df, path = "tables/activities_stats.xlsx")

# FinalFit Table to excel - median or mean?
activities <- c("X..Research.Experiences", "X..Abstracts..Pres..Posters", "X..Peer.Rev.Publications", "X..Volunteer.Experiences", "X..Leadership.Positions", "X..Honored.Clerkships")
degree_list <- c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
activity_list <- list()
for (act in activities) {
  activities_table <- df_clean %>% dplyr::filter(degrees %in% degree_list) %>% 
    summary_factorlist(
      dependent = "degrees", explanatory = c(act), cont = "mean", p = T,
      add_col_totals = TRUE, include_col_totals_percent = TRUE
  )
  activities_table$activity <- act
  activity_list[[act]] <- activities_table
}

# Merging and Exporting to excel
activity_table_df <- dplyr::bind_rows(activity_list)
#write_xlsx(x = activity_table_df, path = "tables/activities_finalfit_mean.xlsx")
```

```{r}
# Exporting activities plots 
#ggsave(plot = honors_clerkships$plot, filename = "figures/honors_clerkships.png", width = 4000, height = 1300, dpi = 300, units = "px")
#ggsave(plot = research_experiences$plot, filename = "figures/research_experiences.png", width = 4000, height = 1300, dpi = 300, units = "px")
#ggsave(plot = abstracts_posters$plot, filename = "figures/abstracts_posters.png", width = 4000, height = 1300, dpi = 300, units = "px")
#ggsave(plot = publications$plot, filename = "figures/publications_plot.png", width = 4000, height = 1300, dpi = 300, units = "px")
#ggsave(plot = volunteering$plot, filename = "figures/volunteering_plot.png", width = 4000, height = 1300, dpi = 300, units = "px")
#ggsave(plot = leadership$plot, filename = "figures/leadership_plot.png", width = 4000, height = 1300, dpi = 300, units = "px")
```

```{r}
# Honors in specialty of choice and couples match (yes/no)
honors_spec <- df_clean %>% dplyr::filter(degrees %in% degree_list) %>% 
  summary_factorlist(
    dependent = "degrees", explanatory = c("Honors.A.This.Specialty", "Couples.Match"), 
    p_cat = "chisq", p = T, 
    add_col_totals = TRUE, include_col_totals_percent = TRUE
  )

# Stats - honors in specialty of choice
honors_list <- list()
dt <- df_clean %>% dplyr::filter(degrees %in% degree_list)
dt <- table(dt$degrees, dt$Honors.A.This.Specialty) %>% as.data.frame.matrix()
print(fisher.test(dt, simulate.p.value = T))
pairwise_fish <- pairwise_fisher_test(dt, p.adjust.method = "fdr", detailed = T)
pairwise_fish$activity <- "honors in specialty"
honors_list[["specialty_honors"]] = pairwise_fish

# Stats - couples match
dt <- df_clean %>% dplyr::filter(degrees %in% degree_list)
dt <- table(dt$degrees, dt$Couples.Match) %>% as.data.frame.matrix()
print(fisher.test(dt, simulate.p.value = T))
pairwise_fish <- pairwise_fisher_test(dt, p.adjust.method = "fdr", detailed = T)
pairwise_fish$activity <- "couples match"
honors_list[["couples_match"]] = pairwise_fish
honors_df <- dplyr::bind_rows(honors_list)

# Exporting dataframes to excel
#write_xlsx(x = honors_spec, path = "tables/specialty_honors_couples_match.xlsx")
#write_xlsx(x = honors_df, path = "tables/specialty_honors_couples_match_pairwise.xlsx")
```



## 4.4 Gap Years

```{r}
# Research Years by degree path
degree_list <- c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
gap_years <- df_clean[df_clean == ""] <- NA
gap_years <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% 
  dplyr::filter(!is.na(Research.Year))
gap_years <- table(gap_years$degrees, gap_years$Research.Year) %>% as.data.frame.matrix()

# Posthoc analysis
fisher.posthoc.research <- pairwise_fisher_test(gap_years, p.adjust.method = "fdr", detailed = T)
fisher.posthoc.research$gap_year <- "research year"

# Year of absence by degree path
degree_list <- c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
gap_years <- df_clean[df_clean == ""] <- NA
gap_years <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% 
  dplyr::filter(!is.na(Absence.Year))
gap_years <- table(gap_years$degrees, gap_years$Absence.Year) %>% as.data.frame.matrix()

# Posthoc analysis
fisher.posthoc.absence <- pairwise_fisher_test(gap_years, p.adjust.method = "fdr", detailed = T)
fisher.posthoc.absence$gap_year <- "year of absence"

# Merging
fisher.posthoc <- dplyr::bind_rows(fisher.posthoc.research, fisher.posthoc.absence)
fisher.posthoc$gap_year <- factor(fisher.posthoc$gap_year, levels = c("research year", "year of absence"))

# Finalfit table
gap_year_degree <- df_clean %>% dplyr::filter(degrees %in% degree_list) %>% 
  summary_factorlist(
    dependent = "degrees", explanatory = c("Research.Year", "Absence.Year"), 
    p_cat = "chisq", p = T, 
    add_col_totals = TRUE, include_col_totals_percent = TRUE
  )

# exports to excel
#write_xlsx(x = fisher.posthoc, path = "tables/gap_year_degree_stats.xlsx")
#write_xlsx(x = gap_year_degree, path = "tables/gap_year_degree.xlsx")
```

```{r}
# Research Years by specialty - plot this on a forest plot! 
degree_list <- c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
gap_years <- df_clean[df_clean == ""] <- NA
gap_years <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% 
  dplyr::filter(!is.na(Research.Year))
gap_years <- table(gap_years$Specialty, gap_years$Research.Year) %>% as.data.frame.matrix()
gap_years <- gap_years[gap_years$No >= 5 & gap_years$Yes >= 5, ]
gap_years <- gap_years[ , c(2, 1)]

# Posthoc analysis
fisher.posthoc.research <- row_wise_fisher_test(gap_years, p.adjust.method = "fdr", detailed = T)
fisher.posthoc.research <- fisher.posthoc.research %>% dplyr::mutate(
  likelihood = dplyr::case_when(
    conf.low > 1 & p.adj < 0.05 ~ "Higher",
    conf.high < 1 & p.adj < 0.05 ~ "Lower",
    p.adj > 0.05 ~ "No Change"
  )
)
fisher.posthoc.research$likelihood <- factor(x = fisher.posthoc.research$likelihood, levels = c("Higher", "No Change", "Lower"))
fisher.posthoc.research$gap_year <- "research year"


# Absence Years by specialty - plot this on a forest plot!
gap_years <- df_clean[df_clean == ""] <- NA
gap_years <- df_clean %>% 
  dplyr::filter(degrees %in% degree_list) %>% 
  dplyr::filter(!is.na(Absence.Year))
gap_years <- table(gap_years$Specialty, gap_years$Absence.Year) %>% as.data.frame.matrix()
gap_years <- gap_years[gap_years$No >= 5 & gap_years$Yes >= 5, ]
gap_years <- gap_years[ , c(2, 1)]

# Posthoc analysis
fisher.posthoc.absence <- row_wise_fisher_test(gap_years, p.adjust.method = "fdr", detailed = T)
fisher.posthoc.absence <- fisher.posthoc.absence %>% dplyr::mutate(
  likelihood = dplyr::case_when(
    conf.low > 1 & p.adj < 0.05 ~ "Higher",
    conf.high < 1 & p.adj < 0.05 ~ "Lower",
    p.adj > 0.05 ~ "No Change"
  )
)
fisher.posthoc.absence$likelihood <- factor(x = fisher.posthoc.absence$likelihood, levels = c("Higher", "No Change", "Lower"))
fisher.posthoc.absence$gap_year <- "year of absence"

# Merging for forest plot
fisher.posthoc <- dplyr::bind_rows(fisher.posthoc.research, fisher.posthoc.absence)
fisher.posthoc$gap_year <- factor(fisher.posthoc$gap_year, levels = c("research year", "year of absence"))

# Finalfit table
gap_year_specialty <- df_clean %>% dplyr::filter(degrees %in% degree_list) %>% 
  summary_factorlist(
    dependent = "Specialty", explanatory = c("Research.Year", "Absence.Year"), 
    p_cat = "chisq", p = F, 
    add_col_totals = TRUE, include_col_totals_percent = TRUE
  )

# exports to excel
#write_xlsx(x = fisher.posthoc, path = "tables/gap_year_specialty_stats.xlsx")
#write_xlsx(x = gap_year_specialty, path = "tables/gap_year_specialty.xlsx")
```

```{r}
# Making a forest plot 
forest_plot <- fisher.posthoc %>% 
  ggplot(aes(x = estimate, xmin = conf.low, xmax = conf.high, y = reorder(group, estimate), color = likelihood)) + 
  geom_point() + 
  geom_errorbarh(height = 0.2) + 
  geom_text(aes(label = p.adj, x = 8), hjust = 0, size = 3) + 
  geom_vline(aes(xintercept = 1), color = "black", linetype = "dashed") + 
  facet_wrap(~gap_year, ncol = 2) + 
  scale_x_continuous(n.breaks = 10, limits = c(0, 10)) +  #2.8
  scale_color_manual(values = c("#eb2323", "#525252", "#2e66ff")) +
  labs(x = "Odds Ratio [95% CI]", y = "Specialty", title = "Odds of Taking a Research Year per Specialty", color = "Odds") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 14),
        strip.background = element_blank(),
        strip.text = element_text(size = 12))
print(forest_plot)

# Saving the plot
#ggsave(plot = forest_plot, filename = "figures/gap_years.png", width = 3500, height = 2500, dpi = 300, units = "px")
```





## 4.5 Honors Societies

```{r}
# aoa status
dual_degrees <- c("MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
aoa_list <- list()
for (degree_path in dual_degrees) {
  aoa <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree_path))
  aoa <- table(aoa$AOA.Sigma, aoa$degrees) %>% as.data.frame.matrix()
  aoa <- aoa[ , c(2, 1)]
  pairwise.fisher <- row_wise_fisher_test(aoa, p.adjust.method = "fdr", detailed = T)
  pairwise.fisher$honors_society <- "AOA"
  pairwise.fisher$dual_degree <- degree_path
  aoa_list[[degree_path]] <- pairwise.fisher
}
aoa_df <- dplyr::bind_rows(aoa_list)

# gold humanism status
dual_degrees <- c("MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")
ghhs_list <- list()
for (degree_path in dual_degrees) {
  ghhs <- df_clean %>% dplyr::filter(degrees %in% c("MD", degree_path))
  ghhs <- table(ghhs$GHHS, ghhs$degrees) %>% as.data.frame.matrix()
  ghhs <- ghhs[ , c(2, 1)]
  pairwise.fisher <- row_wise_fisher_test(ghhs, p.adjust.method = "fdr", detailed = T)
  pairwise.fisher$honors_society <- "Gold Humanism"
  pairwise.fisher$dual_degree <- degree_path
  ghhs_list[[degree_path]] <- pairwise.fisher
}
ghhs_df <- dplyr::bind_rows(ghhs_list)

# Merging
honors_df <- dplyr::bind_rows(list(aoa_df, ghhs_df))

# Finalfit table
honors_ff <- df_clean %>% 
  dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")) %>% 
  summary_factorlist(
    dependent = "degrees", explanatory = c("AOA.Sigma", "GHHS"), 
    p = T, p_cat = "chisq",
    add_col_totals = TRUE, include_col_totals_percent = TRUE
  )

# Exporting to excel 
#write_xlsx(x = honors_df, path = "tables/honors_societies_stats.xlsx")
#write_xlsx(x = honors_ff, path = "tables/honors_societies_table.xlsx")
```



# 5. Match Outcomes

## 5.1 Overall Match

```{r}
# Do MD/PhD students have a higher chance of matching?
overall_match_df <- df_clean %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc"))
overall_match <- as.data.frame.matrix(table(overall_match_df$degrees, overall_match_df$Matched))
overall_match <- overall_match %>% dplyr::filter(Yes >= 5 & No >= 5)

# Chi square and fisher
#chisq.test(overall_match)
fisher.test(overall_match, simulate.p.value = T)

# Post hoc analysis
match_rate_fisher <- pairwise_fisher_test(overall_match, p.adjust.method = "fdr", detailed = T)

# Table for export
table1 <- overall_match_df %>% 
  summary_factorlist(
    dependent = "degrees", explanatory = c("Matched", "Applied_Total", "InterviewOffer_Total", "X..Interviews.Attended"),
    add_col_totals = TRUE, include_col_totals_percent = TRUE, 
    p = TRUE, cont = "median", p_cat = "chisq"
  )

# Exporting to excel
#write_xlsx(x = table1, path = "tables/match_apps.xlsx")
```

## 5.2 Interviews (unadjusted)

```{r}
# Interview info
cols_to_keep <- c("Applied_Total", "InterviewOffer_Total", "Majority.of.Interview.Offers", "Majority.of.Interviews.Attended", "X..Interviews.Attended", "degrees")
overall_interview_df <- df_clean[, cols_to_keep] %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc"))

# Numerical Variables for interviews
interview_int_df <- tidyr::pivot_longer(data = overall_interview_df[, c(1, 2, 5, 6)], cols = c("Applied_Total", "InterviewOffer_Total", "X..Interviews.Attended"), names_to = "interview_metric", values_to = "values")
interview_int_df$interview_metric <- plyr::mapvalues(x = interview_int_df$interview_metric, from = c("Applied_Total", "InterviewOffer_Total", "X..Interviews.Attended"), to = c("Applications", "Interview Offers", "Interviews Attended"))
interview_int_df$degrees <- factor(x = interview_int_df$degrees, levels = c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc"))

# Testing for normality and equal variances - THIS IS NON-NORMAL Data! 
#ggqqplot(overall_interview_df$X..Interviews.Attended)
#shapiro.test(overall_interview_df$Applied_Total)
#leveneTest(X..Interviews.Attended ~ degrees, overall_interview_df)

# Kruskal-Wallis test and post hoc analysis: Total Applications
kruskal_res <- kruskal.test(Applied_Total ~ degrees, data = overall_interview_df)
pairwise_kruskal <- pairwise.wilcox.test(overall_interview_df$Applied_Total, overall_interview_df$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)

# Kruskal-Wallis test and post hoc analysis: Interview offers
kruskal_res <- kruskal.test(InterviewOffer_Total ~ degrees, data = overall_interview_df)
pairwise_kruskal <- pairwise.wilcox.test(overall_interview_df$InterviewOffer_Total, overall_interview_df$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)

# Kruskal-Wallis test and post hoc analysis: Interviews attended
kruskal_res <- kruskal.test(X..Interviews.Attended ~ degrees, data = overall_interview_df)
pairwise_kruskal <- pairwise.wilcox.test(overall_interview_df$X..Interviews.Attended, overall_interview_df$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)
```

```{r}
# Plotting applications, interview offers, and interviews attended
interview_plot <- interview_int_df %>% ggplot(aes(x = degrees, y = values, fill = degrees)) + 
  geom_boxplot(outliers = F) + 
  facet_wrap(~interview_metric, ncol = 3, scales = "free_y") +
  scale_fill_brewer(palette = "Set3") +
  labs(x = "", y = "Number of Occurrences", fill = "Degrees", title = "Number of Applications and Interviews per Degree Path") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(interview_plot)

# exporting figure
#ggsave(plot = interview_plot, filename = "figures/interview_plot.pdf", width = 2800, height = 1500, dpi = 300, units = "px")
```

```{r}
# Function to extract the results of a regression model
model_extracter <- function(m, zt, test_name = NULL) {
  # Summary of the model
  print(summary(m))
  
  # Extract coefficients as a dataframe
  coef_df <- data.frame(
    term = names(coef(m)),
    estimate = coef(m),
    std_error = summary(m)$coefficients[,"Std. Error"],
    zt_value = summary(m)$coefficients[, paste0(zt, " value")],
    p_value = summary(m)$coefficients[, paste0("Pr(>|", zt, "|)")]
  )
  
  # Calculate odds ratios and confidence intervals
  coef_df$odds_ratio <- exp(coef_df$estimate)
  
  # Calculate 95% confidence intervals for odds ratios
  coef_df$ci_lower <- exp(coef_df$estimate - 1.96 * coef_df$std_error)
  coef_df$ci_upper <- exp(coef_df$estimate + 1.96 * coef_df$std_error)
  
  # Round numeric columns to 3 decimal places
  coef_df$term <- NULL
  coef_df_rownames <- row.names(coef_df)
  coef_df <- sapply(coef_df, as.numeric) %>% as.data.frame()
  coef_df$terms <- coef_df_rownames
  coef_df$test <- test_name
  
  # Returning
  return(coef_df)
}

```

```{r}
# Fitting a linear model with interaction of degree path
model <- lm(X..Interviews.Attended ~ Applied_Total * degrees, data = overall_interview_df)

model_df <- model_extracter(m = model, zt = "t")

# Exporting to excel
#write_xlsx(x = coef_df, path = "tables/applications_interviews_linreg.xlsx", )
```

```{r}
# Finding the quantiles to plot (we don't want to include huge outliers with 200+ applications)
#quantile(x = overall_interview_df$Applied_Total, probs = c(0.01, 0.05, 0.25, 0.5, 0.75, 0.90, 0.95, 0.99))
#quantile(x = overall_interview_df$X..Interviews.Attended, probs = c(0.01, 0.05, 0.25, 0.5, 0.75, 0.90, 0.95, 0.99))

# Plotting linear regression lines
overall_interview_df$degrees <- factor(x = overall_interview_df$degrees, levels = c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc"))
lin_reg_plot <- overall_interview_df %>% ggplot(aes(x = Applied_Total, y = X..Interviews.Attended, color = degrees)) +
  geom_smooth(method = "lm", se = T, fill = "lightgrey") + 
  scale_color_brewer(palette = "Dark2") +
  coord_cartesian(xlim = c(0, 140), ylim = c(5, 25)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 7), expand = c(0, 0)) + 
  scale_y_continuous(breaks = scales::pretty_breaks(n = 6), expand = c(0, 0)) + 
  labs(title = "Linear Regression per Degree", x = "Total Applications", y = "Interviews Attended", color = "Degrees") + 
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5))
print(lin_reg_plot)

# exporting figure
#ggsave(plot = lin_reg_plot, filename = "figures/linear_regression_plot.pdf", width = 1600, height = 1000, dpi = 300, units = "px")
```



## 5.3 Interviews (normalized)

```{r}
# Calculating mean, stdev, median, and IQR for applications, interview offers, and interviews attended per specialty
spec.app.counts <- df_clean %>% 
  dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")) %>% 
  dplyr::group_by(Specialty) %>% 
  dplyr::summarise(
    specialty_counts = n(),
    mean_applications = mean(Applied_Total, na.rm = T),
    stdev_applications = sd(Applied_Total, na.rm = T),
    median_applications = median(Applied_Total, na.rm = T),
    iqr_applications = IQR(Applied_Total, na.rm = T),
    mean_interview_offers = mean(InterviewOffer_Total, na.rm = T),
    stdev_interview_offers = sd(InterviewOffer_Total, na.rm = T),
    median_interview_offers = median(InterviewOffer_Total, na.rm = T),
    iqr_interview_offers = IQR(InterviewOffer_Total, na.rm = T),
    mean_interviews_attended = mean(X..Interviews.Attended, na.rm = T),
    stdev_interviews_attended = sd(X..Interviews.Attended, na.rm = T),
    median_interviews_attended = median(X..Interviews.Attended, na.rm = T),
    iqr_interviews_attended = IQR(X..Interviews.Attended, na.rm = T),
  )

# Filtering specialtys with too low counts to be reliable
spec.app.counts <- spec.app.counts[spec.app.counts$specialty_counts >= 10, ]

# Exporting to excel
#write_xlsx(x = spec.app.counts, path = "tables/summarized_app_interview_counts.xlsx")
```

```{r}
# Min-max normalizing after log transformation for right-skewed data. For applications, interview offers, and interviews attended for each specialty
norm.apps.df <- merge(df_clean, spec.app.counts, by = "Specialty", all.x = T)
norm.apps.df <- norm.apps.df %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc"))

# Log transformed min-max scaling (good for right-skewed data)
norm.apps.df$norm_applied_total <- ave(norm.apps.df$Applied_Total, norm.apps.df$Specialty,
                                       FUN = function(x) {
                                         logged <- log1p(x)
                                         (logged - min(logged, na.rm = T)) / (max(logged, na.rm = T) - min(logged, na.rm = T))
                                       })

norm.apps.df$norm_interview_offers <- ave(norm.apps.df$InterviewOffer_Total, norm.apps.df$Specialty,
                                          FUN = function(x) {
                                            logged <- log1p(x)
                                            (logged - min(logged, na.rm = T)) / (max(logged, na.rm = T) - min(logged, na.rm = T))
                                            })

norm.apps.df$norm_interviews_attend <- ave(norm.apps.df$X..Interviews.Attended, norm.apps.df$Specialty,
                                           FUN = function(x) {
                                             logged <- log1p(x)
                                             (logged - min(logged, na.rm = T)) / (max(logged, na.rm = T) - min(logged, na.rm = T))
                                             })

# Factoring
norm.apps.df$degrees <- factor(x = norm.apps.df$degrees, levels = c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc"))
```

```{r}
# Statistics for normalized interview metrics
# Kruskal-Wallis test and post hoc analysis: Total Applications
kruskal_res <- kruskal.test(norm_applied_total ~ degrees, data = norm.apps.df)
pairwise_kruskal <- pairwise.wilcox.test(norm.apps.df$norm_applied_total, norm.apps.df$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)

# Kruskal-Wallis test and post hoc analysis: Interview offers
kruskal_res <- kruskal.test(norm_interview_offers ~ degrees, data = norm.apps.df)
pairwise_kruskal <- pairwise.wilcox.test(norm.apps.df$norm_interview_offers, norm.apps.df$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)

# Kruskal-Wallis test and post hoc analysis: Interviews attended
kruskal_res <- kruskal.test(norm_interviews_attend ~ degrees, data = norm.apps.df)
pairwise_kruskal <- pairwise.wilcox.test(norm.apps.df$norm_interviews_attend, norm.apps.df$degrees, p.adjust.method = "fdr")
print(kruskal_res)
print(pairwise_kruskal)
```

```{r}
# Cleaning data for plotting
cols_to_keep <- c("degrees", "norm_applied_total", "norm_interview_offers", "norm_interviews_attend")
norm.plot.df <- norm.apps.df[ , cols_to_keep] %>% tidyr::pivot_longer(cols = c("norm_applied_total", "norm_interview_offers", "norm_interviews_attend"), names_to = "interview_metric", values_to = "values")
norm.plot.df$interview_metric <- plyr::mapvalues(x = norm.plot.df$interview_metric, from = c("norm_applied_total", "norm_interview_offers", "norm_interviews_attend"), to = c("Applications", "Interview Offers", "Interviews Attended"))
norm.plot.df$interview_metric <- factor(x = norm.plot.df$interview_metric, levels = c("Applications", "Interview Offers", "Interviews Attended"))

# Plotting Normalized applications, interview offers, and interviews attended
interview_plot <- norm.plot.df %>% ggplot(aes(x = degrees, y = values, fill = degrees)) + 
  geom_boxplot(outliers = F) + 
  facet_wrap(~interview_metric, ncol = 3, scales = "free_y") +
  scale_fill_brewer(palette = "Set3") +
  labs(x = "", y = "Normalized Number of Occurrences", fill = "Degrees", title = "Normalized Number of Applications and Interviews") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5))
print(interview_plot)

# exporting figure
#ggsave(plot = interview_plot, filename = "figures/interview_plot_normalized.pdf", width = 2800, height = 1500, dpi = 300, units = "px")
```



## 5.4 Signals, geographic connections, geographic preferences, and away rotations

```{r}
# Importing the matched doximity programs file
pg <- read.csv(file = "tables/STAR_Programs_2017_2023_final_matched.csv", na.strings = "")

# Filtering for students who matched
matched_ids <- df_clean %>% 
  dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")) %>% 
  dplyr::filter(Matched == "Yes") %>% 
  dplyr::filter(Survey.Year >= 2021) %>% 
  dplyr::pull(STAR.ID)

pg.filt <- pg %>% dplyr::filter(STAR.ID %in% matched_ids)

# Filtering for non-NA values and factoring
#pg.filt <- pg.filt[!is.na(pg.filt$Signaled.Program), ]
pg.filt$Matched <- factor(x = pg.filt$Matched, levels = c("N", "Y"))
pg.filt$Signaled.Program <- factor(x = pg.filt$Signaled.Program, levels = c("N", "Y"))
pg.filt$Interview.Offer <- factor(x = pg.filt$Interview.Offer, levels = c("N", "Y"))
pg.filt$Geographic.Connection <- factor(x = pg.filt$Geographic.Connection, levels = c("N", "Y"))
pg.filt$Geographic.Preference.ERAS.Supp.App <- factor(x = pg.filt$Geographic.Preference.ERAS.Supp.App, levels = c("N", "Y"))
pg.filt$Away.Rotation <- factor(x = pg.filt$Away.Rotation, levels = c("N", "Y"))
pg.filt$degrees <- factor(x = pg.filt$degrees, levels = c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc"))
```

```{r}
# LR on Interview Offers
model_outcome_list <- list()

# Logistic regression of signaling - univariate
model <- glm(Interview.Offer ~ Signaled.Program, data = pg.filt, family = "binomial")
model_outcome_list[["signaled program univariate"]] <- model_extracter(m = model, zt = "z", test_name = "signaled program univariate")

# Logistic regression of Geographic Connection - univariate
model <- glm(Interview.Offer ~ Geographic.Connection, data = pg.filt, family = "binomial")
model_outcome_list[["geographic connection univariate"]] <- model_extracter(m = model, zt = "z", test_name = "geographic connection univariate")

# Logistic regression of Geographic Preference - univariate
model <- glm(Interview.Offer ~ Geographic.Preference.ERAS.Supp.App, data = pg.filt, family = "binomial")
model_outcome_list[["geographic preference univariate"]] <- model_extracter(m = model, zt = "z", test_name = "geographic preference univariate")

# Logistic regression of Away Rotations - univariate
model <- glm(Interview.Offer ~ Away.Rotation, data = pg.filt, family = "binomial")
model_outcome_list[["away rotation univariate"]] <- model_extracter(m = model, zt = "z", test_name = "away rotation univariate")

# Multivariate without interactors
model <- glm(Interview.Offer ~ Signaled.Program + Geographic.Connection + Geographic.Preference.ERAS.Supp.App + Away.Rotation, data = pg.filt, family = "binomial")
model_outcome_list[["multivariate"]] <- model_extracter(m = model, zt = "z", test_name = "multivariate")

# Multivariate WITH degree path as interactors
model <- glm(Interview.Offer ~ Signaled.Program * degrees + Geographic.Connection * degrees + Geographic.Preference.ERAS.Supp.App * degrees + Away.Rotation * degrees, data = pg.filt, family = "binomial")
model_outcome_list[["multivariate with interactors"]] <- model_extracter(m = model, zt = "z", test_name = "multivariate with interactors")

# Making a fancy table to export to word
#fancy_table <- tbl_regression(model, exponentiate = T, show_single_row = c("Signaled.Program", "Geographic.Connection", "Geographic.Preference.ERAS.Supp.App", "Away.Rotation"))
#fancy_table %>% as_flex_table() %>% save_as_docx(path = "tables/interview_offers_logistic_regression.docx")

# Merging all results together
model_df_interviews <- dplyr::bind_rows(model_outcome_list)
model_df_interviews$outcome <- "interview_offer"

# Checking residuals using DHARMa
#simulation_df <- simulateResiduals(model, plot = T)

# Exporting the dataframe
#write_xlsx(x = model_df_interviews, path = "tables/interview_offers_logistic_regression.xlsx")
```

```{r}
# LR on Matches
model_outcome_list <- list()

# Logistic regression of signaling - univariate
model <- glm(Matched ~ Signaled.Program, data = pg.filt, family = "binomial")
model_outcome_list[["signaled program univariate"]] <- model_extracter(m = model, zt = "z", test_name = "signaled program univariate")

# Logistic regression of Geographic Connection - univariate
model <- glm(Matched ~ Geographic.Connection, data = pg.filt, family = "binomial")
model_outcome_list[["geographic connection univariate"]] <- model_extracter(m = model, zt = "z", test_name = "geographic connection univariate")

# Logistic regression of Geographic Preference - univariate
model <- glm(Matched ~ Geographic.Preference.ERAS.Supp.App, data = pg.filt, family = "binomial")
model_outcome_list[["geographic preference univariate"]] <- model_extracter(m = model, zt = "z", test_name = "geographic preference univariate")

# Logistic regression of Away Rotations - univariate
model <- glm(Matched ~ Away.Rotation, data = pg.filt, family = "binomial")
model_outcome_list[["away rotation univariate"]] <- model_extracter(m = model, zt = "z", test_name = "away rotation univariate")

# Multivariate without interactors
model <- glm(Matched ~ Signaled.Program + Geographic.Connection + Geographic.Preference.ERAS.Supp.App + Away.Rotation, data = pg.filt, family = "binomial")
model_outcome_list[["multivariate"]] <- model_extracter(m = model, zt = "z", test_name = "multivariate")

# Multivariate WITH degree path as interactors
model <- glm(Matched ~ Signaled.Program * degrees + Geographic.Connection * degrees + Geographic.Preference.ERAS.Supp.App * degrees + Away.Rotation * degrees, data = pg.filt, family = "binomial")
model_outcome_list[["multivariate with interactors"]] <- model_extracter(m = model, zt = "z", test_name = "multivariate with interactors")

# Making a fancy table to export to word
#fancy_table <- tbl_regression(model, exponentiate = T, show_single_row = c("Signaled.Program", "Geographic.Connection", "Geographic.Preference.ERAS.Supp.App", "Away.Rotation"))
#fancy_table %>% as_flex_table() %>% save_as_docx(path = "tables/matches_logistic_regression.docx")

# Merging all results together
model_df_matches <- dplyr::bind_rows(model_outcome_list)
model_df_matches$outcome <- "match"

# Checking residuals using DHARMa
#simulation_df <- simulateResiduals(model, plot = T)

# Exporting the dataframe
#write_xlsx(x = model_df_matches, path = "tables/matches_logistic_regression.xlsx")
```

```{r}
# Graphing Odds Ratios for interview offers and matched based on signaling, geographic connections, geographic preferences, and away rotations (with degree path as an interactor)
model_df <- dplyr::bind_rows(model_df_interviews, model_df_matches)

# Making new names for terms
terms <- c("Signaled.ProgramY", "Geographic.ConnectionY", 
           "Geographic.Preference.ERAS.Supp.AppY", "Away.RotationY",
           "degreesMD-PhD", "degreesMD-MPH", "degreesMD-MBA", "degreesMD-MSc",
           "Signaled.ProgramY:degreesMD-PhD", "Signaled.ProgramY:degreesMD-MPH",
           "Signaled.ProgramY:degreesMD-MBA", "Signaled.ProgramY:degreesMD-MSc",
           "degreesMD-PhD:Geographic.ConnectionY", 
           "degreesMD-MPH:Geographic.ConnectionY",
           "degreesMD-MBA:Geographic.ConnectionY", 
           "degreesMD-MSc:Geographic.ConnectionY",
           "degreesMD-PhD:Geographic.Preference.ERAS.Supp.AppY",
           "degreesMD-MPH:Geographic.Preference.ERAS.Supp.AppY",
           "degreesMD-MBA:Geographic.Preference.ERAS.Supp.AppY",
           "degreesMD-MSc:Geographic.Preference.ERAS.Supp.AppY",
           "degreesMD-PhD:Away.RotationY", "degreesMD-MPH:Away.RotationY",
           "degreesMD-MBA:Away.RotationY", "degreesMD-MSc:Away.RotationY")

new_terms <- c("Signaled Program", "Geographic Connection", "Geographic Preference", "Away Rotation",
               "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc",
               "Signaled Program × MD-PhD", "Signaled Program × MD-MPH",
               "Signaled Program × MD-MBA", "Signaled Program × MD-MSc",
               "Geographic Connection × MD-PhD", "Geographic Connection × MD-MPH",
               "Geographic Connection × MD-MBA", "Geographic Connection × MD-MSc",
               "Geographic Preference × MD-PhD", "Geographic Preference × MD-MPH",
               "Geographic Preference × MD-MBA", "Geographic Preference × MD-MSc",
               "Away Rotation × MD-PhD", "Away Rotation × MD-MPH",
               "Away Rotation × MD-MBA", "Away Rotation × MD-MSc")

# Tidying before plotting
model_df <- model_df %>% 
  dplyr::filter(test == "multivariate with interactors") %>% 
  dplyr::filter(terms != "(Intercept)")

model_df$terms <- plyr::mapvalues(x = model_df$terms, from = terms, to = new_terms)
model_df$terms <- factor(x = model_df$terms, levels = rev(new_terms))
model_df$outcome <- factor(model_df$outcome, levels = c("interview_offer", "match"))
model_df <- model_df %>% dplyr::mutate(
  regulation = dplyr::case_when(
    ci_lower > 1 & p_value < 0.05 ~ "Overrepresented",
    ci_upper < 1 & p_value < 0.05 ~ "Underrepresented",
    p_value >= 0.05 ~ "not significant"
  )
)
model_df$regulation <- factor(model_df$regulation, levels = c("Overrepresented", "Underrepresented", "not significant"))
model_df$p_value <- format(x = model_df$p_value, digits = 2)
```

```{r}
# Plotting a forest plot
forest_plot <- model_df %>% 
  ggplot(aes(x = odds_ratio, xmin = ci_lower, xmax = ci_upper, y = terms, color = regulation)) + 
  geom_point() + 
  geom_errorbarh(height = 0.2) + 
  #geom_text(aes(label = p_value, x = 18), hjust = 0, size = 3) + 
  facet_wrap(~outcome, ncol = 2) +
  geom_vline(aes(xintercept = 1), color = "black", linetype = "dashed") + 
  scale_x_continuous(n.breaks = 5, limits = c(0, 17)) +
  scale_color_manual(values = c("#eb2323", "#2e66ff", "#525252")) +
  labs(x = "Odds Ratio [95% CI]", y = "Predictors", title = "Logistic Regression: Interview Offers and Matches", color = "Odds") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 12),
        strip.background = element_blank())
print(forest_plot)

# Saving the figure
#ggsave(plot = forest_plot, filename = "figures/logistic_regression_interviews_matches.pdf", width = 2400, height = 2400, dpi = 300, units = "px")
```

```{r}
# Feature Importances for multivariate LR predicting interview offers with degree path as interactors
model_interviews <- glm(Interview.Offer ~ Signaled.Program + Geographic.Connection + Geographic.Preference.ERAS.Supp.App + Away.Rotation, data = pg.filt, family = "binomial")
car::Anova(model_interviews)

# Feature Importances for multivariate LR predicting matches with degree path as interactors
model_matches <- glm(Matched ~ Signaled.Program + Geographic.Connection + Geographic.Preference.ERAS.Supp.App + Away.Rotation, data = pg.filt, family = "binomial")
car::Anova(model_matches)
```



# 6. Match Outcomes

## 6.1 Specialty outcomes

```{r}
# Function for performing fisher's exact test comparing MD vs other dual degree options

md_fisher <- function(comparision, dual_degree) {
  # Making a contingency table for MD and dual degree students
  dual_conting <- df_clean %>% dplyr::filter(degrees %in% c("MD", dual_degree))  #"MD-PhD", "MD-MPH", "MD-MSc"
  dual_conting <- table(dual_conting[[comparison]], dual_conting$degrees) %>% as.data.frame.matrix()
  dual_conting <- dual_conting %>% dplyr::filter(.[[1]] >= 5 & .[[2]] >= 5)
  dual_conting <- dual_conting[, c(2, 1)]
  
  # Chi Squared test and fisher's exact test to see if specialty choice is different between MD and MD-PhD
  #chi_res <- chisq.test(dual_conting)
  fish_res <- fisher.test(dual_conting, simulate.p.value = T)
  print(fish_res)
  
  # Posthoc tests for chi square and fisher 
  #chi.posthoc <- chisq.posthoc.test(dual_conting, method = "fdr")
  fisher.posthoc <- row_wise_fisher_test(dual_conting, p.adjust.method = "fdr", detailed = T)
  
  return(fisher.posthoc)
}
```

```{r}
# Specialty outcomes
mdphd_fisher <- md_fisher(comparision = "Specialty", dual_degree = "MD-PhD")
mdphd_fisher$degree <- "MD-PhD (n = 1239)"
mdphd_fisher$mdphd_p_adj <- mdphd_fisher$p.adj
mdphd_fisher$mdphd_or_ci <- paste0(signif(mdphd_fisher$estimate, digits = 2), " [", signif(mdphd_fisher$conf.low, digits = 2), "-", signif(mdphd_fisher$conf.high, digits = 2), "]")

mdmph_fisher <- md_fisher(comparision = "Specialty", dual_degree = "MD-MPH")
mdmph_fisher$degree <- "MD-MPH (n = 1797)"
mdmph_fisher$mdmph_p_adj <- mdmph_fisher$p.adj
mdmph_fisher$mdmph_or_ci <- paste0(signif(mdmph_fisher$estimate, digits = 2), " [", signif(mdmph_fisher$conf.low, digits = 2), "-", signif(mdmph_fisher$conf.high, digits = 2), "]")

mdmsc_fisher <- md_fisher(comparision = "Specialty", dual_degree = "MD-MSc")
mdmsc_fisher$degree <- "MD-MSc (n = 2551)"
mdmsc_fisher$mdmsc_p_adj <- mdmsc_fisher$p.adj
mdmsc_fisher$mdmsc_or_ci <- paste0(signif(mdmsc_fisher$estimate, digits = 2), " [", signif(mdmsc_fisher$conf.low, digits = 2), "-", signif(mdmsc_fisher$conf.high, digits = 2), "]")

# Filtering for the same specialties
specs <- c(mdphd_fisher$group, mdmph_fisher$group, mdmsc_fisher$group)
specs_count <- table(specs)
specs_count <- specs_count[specs_count > 1]
specs_to_keep <- specs[specs %in% names(specs_count)] %>% unique()

# Merging Specialty outcomes
specialty <- dplyr::bind_rows(list(mdphd_fisher[, c(1:11)], mdmph_fisher[, c(1:11)], mdmsc_fisher[, c(1:11)]))
specialty <- specialty[specialty$group %in% specs_to_keep, ]
specialty$degree <- factor(x = specialty$degree, levels = c("MD-PhD (n = 1239)", "MD-MPH (n = 1797)", "MD-MSc (n = 2551)"))
specialty$p.adj <- signif(x = specialty$p.adj, digits = 2)

# Table for export
table2 <- df_clean %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
  summary_factorlist(
    dependent = "degrees", explanatory = c("Specialty")
    #add_col_totals = TRUE, include_col_totals_percent = TRUE, 
    #p = TRUE, cont = "median", p_cat = "chisq"
  )
table2$label <- NULL
colnames(table2) <- c("group", "MD_percent", "MD-MPH_percent", "MD-MSc_percent", "MD-PhD_percent")
table2 <- merge(table2, mdphd_fisher[, c(1, 12, 13)], on = "group", all.x = T)
table2 <- merge(table2, mdmph_fisher[, c(1, 12, 13)], on = "group", all.x = T)
table2 <- merge(table2, mdmsc_fisher[, c(1, 12, 13)], on = "group", all.x = T)

# Exporting to excel
#write_xlsx(x = table2, path = "tables/specialties.xlsx")
```

```{r}
# Making a forest plot 
forest_plot <- specialty %>% 
  ggplot(aes(x = estimate, xmin = conf.low, xmax = conf.high, y = reorder(group, estimate), color = degree)) + 
  geom_point() + 
  geom_errorbarh(height = 0.2) + 
  geom_text(aes(label = p.adj, x = 8), hjust = 0, size = 3) + 
  geom_vline(aes(xintercept = 1), color = "#5e5e5e", linetype = "dashed") + 
  facet_wrap(~degree, ncol = 3) +
  scale_x_continuous(n.breaks = 10, limits = c(0, 10)) +  #2.8
  scale_color_manual(values = c("#0053cf", "#cf3e00", "#cfb700")) +
  labs(x = "Odds Ratio [95% CI]", y = "Specialty", title = "Specialty Outcomes for Different Dual Degrees Relative to MD-Only", color = "Dual Degree") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 12))
print(forest_plot)

# exporting figure
#ggsave(plot = forest_plot, filename = "figures/specialty_forest_plot2.png", width = 3500, height = 2000, dpi = 300, units = "px")
```

```{r}
# Making a contingency table for MD and MD-PhD Students
mdphd_conting <- df_clean %>% dplyr::filter(degrees %in% c("MD", "MD-PhD"))  #"MD-MPH", "MD-MSc"
mdphd_conting <- table(mdphd_conting$Specialty, mdphd_conting$degrees) %>% as.data.frame.matrix()
mdphd_conting <- mdphd_conting %>% dplyr::filter(MD >= 5 & `MD-PhD` >= 5)
mdphd_conting <- mdphd_conting[, c(2, 1)]

# Chi Squared test and fisher's exact test to see if specialty choice is different between MD and MD-PhD
chi_res <- chisq.test(mdphd_conting)
fish_res <- fisher.test(mdphd_conting, simulate.p.value = T)
print(fish_res)

# Posthoc tests for chi square and fisher 
chi.posthoc <- chisq.posthoc.test(mdphd_conting, method = "fdr")
fisher.posthoc <- row_wise_fisher_test(mdphd_conting, p.adjust.method = "fdr", detailed = T)
```



## 6.2 AAMC MD/PhD Correlations in Specialties

```{r}
# Importing data from AAMC
aamc <- read_xlsx("AAMC_data/AAMC_Table-B4_processed.xlsx")
aamc_totals <- aamc[aamc$specialties == "Total", ]
aamc_totals$total_active_nomdphd <- aamc_totals$total_active - aamc_totals$mdphd_active
aamc <- aamc[aamc$specialties != "Total", ]
```

```{r}
# Tidying for plotting
aamc_totals_plot <- aamc_totals
aamc_totals_plot$percent_change_totals <- ((aamc_totals_plot$total_active_nomdphd - 78959) / 78959) * 100
aamc_totals_plot$percent_change_mdphd <- ((aamc_totals_plot$mdphd_active - 2806) / 2806) * 100
aamc_totals_plot <- aamc_totals_plot %>% 
  tidyr::pivot_longer(cols = c("percent_change_mdphd", "percent_change_totals"), names_to = "degree", values_to = "percent_change")
aamc_totals_plot$degree <- plyr::mapvalues(x = aamc_totals_plot$degree, from = c("percent_change_mdphd", "percent_change_totals"), to = c("MD-PhD", "Total (excluding MD-PhD)"))
aamc_totals_plot$degree <- factor(x = aamc_totals_plot$degree, levels = c("MD-PhD", "Total (excluding MD-PhD)"))

# Plotting total MD/PhD and total MD
aamc_totals_plot <- aamc_totals_plot %>% 
  ggplot(aes(x = year, y = percent_change, color = degree)) + 
  geom_line() + 
  geom_point() + 
  scale_x_continuous(breaks = seq(min(aamc_totals_plot$year), max(aamc_totals_plot$year), by = 1)) + 
  #facet_wrap(~degree) + 
  labs(y = "percent change (%)", color = "Degree") + 
  theme_classic() + 
  theme(strip.background = element_blank())
print(aamc_totals_plot)

# Saving the plot
#ggsave(plot = aamc_totals_plot, filename = "figures/AAMC_totals_overtime.png", width = 2300, height = 1500, dpi = 300, units = "px")
```

```{r}
specialties_interest <- c("Anesthesiology", "Allergy and Immunology", "Child Neurology", "Dermatology", "Emergency Medicine", "Family Medicine", "Internal Medicine", "Medical Genetics and Genomics",  "Neurological Surgery", "Neurology", "Obstetrics and Gynecology", "Ophthalmology", "Orthopaedic Surgery", "Otolaryngology", "Pathology", "Pediatrics", "Physical Medicine and Rehabilitation", "Plastic Surgery", "Psychiatry", "Radiation Oncology", "Radiology: Diagnostic", "Radiology, Interventional: Integrated",  "Surgery: General", "Urology", "Vascular Surgery: Integrated")

aamc_filt <- aamc[aamc$specialties %in% specialties_interest, ]
aamc_filt$total_active_nomdphd <- aamc_filt$total_active - aamc_filt$mdphd_active
aamc_filt <- aamc_filt %>% tidyr::pivot_longer(cols = c("mdphd_active", "total_active_nomdphd"), names_to = "degree", values_to = "counts")
aamc_filt$degree <- plyr::mapvalues(x = aamc_filt$degree, from = c("mdphd_active", "total_active_nomdphd"), to = c("MD-PhD", "Total (excluding MD-PhD)"))
aamc_filt$degree <- factor(x = aamc_filt$degree, levels = c("MD-PhD", "Total (excluding MD-PhD)"))
aamc_filt <- aamc_filt %>% group_by(specialties, degree) %>% 
  dplyr::summarise(specialty_counts = mean(counts, na.rm = TRUE))
aamc_filt$specialty_counts <- round(aamc_filt$specialty_counts)
aamc_filt <- aamc_filt %>% tidyr::pivot_wider(names_from = "degree", values_from = "specialty_counts")

# Making a dataframe matrix 
aamc_filt <- aamc_filt %>% tibble::column_to_rownames(var = "specialties") %>% as.data.frame.matrix()
```

```{r}
# Stats
fish.results <- fisher.test(aamc_filt, simulate.p.value = T)
chi.results <- chisq.test(aamc_filt)
#print(chi.results)

# Posthoc stats
fish.posthoc <- row_wise_fisher_test(aamc_filt, p.adjust.method = "fdr", detailed = T)
fish.posthoc <- fish.posthoc %>% dplyr::mutate(
  representation = dplyr::case_when(
    p.adj < 0.05 & conf.low > 1 ~ "MD-PhD Overepresented",
    p.adj < 0.05 & conf.high < 1 ~ "MD-PhD Underrepresented",
    p.adj > 0.05 ~ "not significant"
  )
)
fish.posthoc$representation <- factor(fish.posthoc$representation, levels = c("MD-PhD Overepresented", "MD-PhD Underrepresented", "not significant"))
```

```{r}
# Plotting OR and 95% CIs
forest_plot <- fish.posthoc %>% 
  ggplot(aes(x = estimate, xmin = conf.low, xmax = conf.high, y = reorder(group, estimate), color = representation)) + 
  geom_point() + 
  geom_errorbarh(height = 0.2) + 
  geom_text(aes(label = p.adj, x = 8.5), hjust = 0, size = 3) + 
  geom_vline(aes(xintercept = 1), color = "black", linetype = "dashed") + 
  scale_x_continuous(n.breaks = 10, limits = c(0, 10)) +  #2.8
  scale_color_manual(values = c("#cf3e00", "#0053cf", "#5e5e5e")) +
  labs(x = "Odds Ratio [95% CI]", y = "Specialty", title = "Specialty Outcomes for MD-PhD Relative to MD-Only (AAMC Data)", color = "MD-PhD Representation") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 12))
print(forest_plot)

# exporting figure
#ggsave(plot = forest_plot, filename = "figures/aamc_specialty_forest_plot.png", width = 2500, height = 2000, dpi = 300, units = "px")
```



## 6.3 Multiple Logistic Regression for Predicting Match Success

```{r}
# Counts for non-NA columns
non_na_lengths <- apply(df_logit, 2, function(x) length(na.omit(x)))
```

```{r}
# Logistic regression function for individual degrees

logistic_regression <- function(degree, verbose = FALSE) {
  
  # Cleaning the df
  df_degree <- df_clean %>% dplyr::filter(degrees == degree) 
  
  # Fitting the negative binomial regression
  logit_model <- glm(Matched ~ Public_School + IvyP + Applied_Total + step1_centered + step2_centered + X..Honored.Clerkships + Honors.A.This.Specialty + AOA.Sigma + GHHS + Research.Year + Absence.Year + Couples.Match + X..Research.Experiences + X..Abstracts..Pres..Posters + X..Peer.Rev.Publications + X..Volunteer.Experiences + X..Leadership.Positions + Required.to.Remediate + Total.Costs.Centered, data = df_degree, family = "binomial")  # + InterviewOffer_Total
  if (verbose) {
    print(summary(logit_model))
  }

  # Making a dataframe for exporting the results
  model_df <- summary(logit_model)$coefficients %>% as.data.frame()
  colnames(model_df) <- c("estimate", "standard_error", "z_value", "p_value")
  model_df$OR <- exp(model_df$estimate)
  ci_df <- exp(confint(logit_model)) %>% as.data.frame()
  colnames(ci_df) <- c("conf.low", "conf.high")
  model_df <- merge(model_df, ci_df, by=0)
  model_df <- model_df[model_df$Row.names != "(Intercept)", ]
  model_df$degree <- degree
  model_df <- model_df %>% dplyr::mutate(
    likelihood = dplyr::case_when(
      conf.low > 1 & p_value < 0.05 ~ "Higher",
      conf.high < 1 & p_value < 0.05 ~ "Lower",
      p_value > 0.05 ~ "No Change"
    )
  )
  model_df$likelihood <- factor(x = model_df$likelihood, levels = c("Higher", "No Change", "Lower"))
  
  return(model_df)
}
```

```{r}
# Multiple logistic regression for each degree path
logit_md <- logistic_regression(degree = "MD", verbose = F)
logit_mdphd <- logistic_regression(degree = "MD-PhD", verbose = T)
logit_mdmph <- logistic_regression(degree = "MD-MPH", verbose = F)
logit_mdmsc <- logistic_regression(degree = "MD-MSc", verbose = F)

logit_total <- dplyr::bind_rows(list(logit_md, logit_mdphd, logit_mdmph, logit_mdmsc))
```

```{r}
df_logit <- df_clean %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc"))

logit_model <- glm(Matched ~ degrees + Public_School + IvyP + Applied_Total + InterviewOffer_Total + step1_centered + step2_centered + X..Honored.Clerkships + Honors.A.This.Specialty + AOA.Sigma + GHHS + Research.Year + Absence.Year + Couples.Match + X..Research.Experiences + X..Abstracts..Pres..Posters + X..Peer.Rev.Publications + X..Volunteer.Experiences + X..Leadership.Positions + Required.to.Remediate + Total.Costs.Centered, data = df_logit, family = "binomial")
summary(logit_model)
```



## 6.4 Random forest and feature importances

```{r}
# Completed in python - "05_random_forest.ipynb"
```




# 7. Cost Analysis

## 7.1 Negative binomial regression for cost prediction per degree path

```{r}
# Cost analysis 
cost_table <- df_clean %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
  summary_factorlist(dependent = "degrees", explanatory = c("Interview.Cost", "Application.Fees", "Virtual.Interview.Cost", "Other.Costs", "Total.Costs"))
```

```{r}
# Centering interview costs to make them integers
centered_interview_costs <- c("<$1000" = 500, "$1000-$1999" = 1500, "$2000-$2999" = 2500, "$3000-$3999" = 3500, "$4000-$4999" = 4500, "$5000-$5999" = 5500, "$6000-$6999" = 6500, "$7000-$7999" = 7500, "$8000-$8999" = 8500, "$9000-$9999" = 9500, "$10000-$10999" = 10500, "$11000-$11999" = 11500, ">$12000" = 12500)
centered_application_fees <- c("<$500" = 250, "$500-$999" = 750, "$1000-$1499" = 1250, "$1500-$1999" = 1750, "$2000-$2499" = 2250, "$2500-$2999" = 2750, "$3000-$3499" = 3250, ">$3500" = 3750)
centered_virtual_interview_costs <- c("<$50" = 25, "$50-$100" = 75, "$101-$150" = 125, "$151-$200" = 175, "$201-$250" = 225, "$251-$300" = 275, ">$300" = 325)
centered_other_costs <- c("<$1000" = 500, "$1000-$1999" = 1500, "$2000-$2999" = 2500, "$3000-$3999" = 3500, "$4000-$4999" = 4500, "$5000-$5999" = 5500, "$6000-$6999" = 6500, "$7000-$7999" = 7500, "$8000-$8999" = 8500, "$9000-$9999" = 9500, ">$10000" = 10500)
centered_total_costs <- c("<$1000" = 500, "$1000-$1999" = 1500, "$2000-$2999" = 2500, "$3000-$3999" = 3500, "$4000-$4999" = 4500, "$5000-$5999" = 5500, "$6000-$6999" = 6500, "$7000-$7999" = 7500, "$8000-$8999" = 8500, "$9000-$9999" = 9500, "$10000-$10999" = 10500, "$11000-$11999" = 11500, "$12000-$12999" = 12500, "$13000-$13999" = 13500, "$14000-$14999" = 14500, "$15000-$15999" = 15500, "$16000-$16999" = 16500, "$17000-$17999" = 17500, "$18000-$18999" = 18500, "$19000-$19999" = 19500, "$20000-$20999" = 20500, "$21000-$21999" = 21500, "$22000-$22999" = 22500, "$23000-$23999" = 23500, "$24000-$24999" = 24500, ">$25000" = 25500)

# Making new columns with integers for costs
df_clean <- df_clean %>% dplyr::mutate(
  Interview.Cost.Centered = as.numeric(centered_interview_costs[as.character(Interview.Cost)]),
  Application.Fees.Centered = as.numeric(centered_application_fees[as.character(Application.Fees)]),
  Virtual.Interview.Cost.Centered = as.numeric(centered_virtual_interview_costs[as.character(Virtual.Interview.Cost)]),
  Other.Costs.Centered = as.numeric(centered_other_costs[as.character(Other.Costs)]),
  Total.Costs.Centered = as.numeric(centered_total_costs[as.character(Total.Costs)])
)
```

```{r}
# Plotting histograms of centered costs
df_clean %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
  ggplot(aes(x = Total.Costs.Centered)) + 
  geom_histogram(binwidth = 1000)

# Cost analysis with centered costs
cost_table_centered <- df_clean %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
  summary_factorlist(dependent = "degrees", explanatory = c("Interview.Cost.Centered", "Application.Fees.Centered", "Virtual.Interview.Cost.Centered", "Other.Costs.Centered", "Total.Costs.Centered"))
```

```{r}
# Negative binomial regression function
neg_binom_regression <- function(costs, verbose = FALSE) {
  
  # Cleaning the df
  costs_df <- df_clean %>% 
    dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
    dplyr::filter(Sexual.Orientation %in% c("Male", "Female", NA))
  
  # Fitting the negative binomial regression
  model <- glm.nb(costs_df[[costs]] ~ degrees + Age.Group + Sexual.Orientation + Race.Ethnicity + First.Generation.College + Food.Housing.Insecurity + Public_School + IvyP, data = costs_df)
  if (verbose) {
    print(summary(model))
  }

  # Making a dataframe for exporting the results
  model_df <- summary(model)$coefficients %>% as.data.frame()
  colnames(model_df) <- c("estimate", "standard_error", "z_value", "p_value")
  model_df$OR <- exp(model_df$estimate)
  ci_df <- exp(confint(model)) %>% as.data.frame()
  colnames(ci_df) <- c("conf.low", "conf.high")
  model_df <- merge(model_df, ci_df, by=0)
  model_df <- model_df[model_df$Row.names != "(Intercept)", ]
  model_df$cost <- costs
  model_df <- model_df %>% dplyr::mutate(
    likelihood = dplyr::case_when(
      conf.low > 1 & p_value < 0.05 ~ "Higher",
      conf.high < 1 & p_value < 0.05 ~ "Lower",
      p_value > 0.05 ~ "No Change"
    )
  )
  model_df$likelihood <- factor(x = model_df$likelihood, levels = c("Higher", "No Change", "Lower"))
  
  return(model_df)
}
```

```{r}
# Costs negative binomial regressions
costs.total <- neg_binom_regression(costs = "Total.Costs.Centered", verbose = F)
costs.interviews <- neg_binom_regression(costs = "Interview.Cost.Centered", verbose = F)
costs.applications <- neg_binom_regression(costs = "Application.Fees.Centered", verbose = F)
costs.virt.int <- neg_binom_regression(costs = "Virtual.Interview.Cost.Centered", verbose = F)
costs.other <- neg_binom_regression(costs = "Other.Costs.Centered", verbose = F)

# Merging and cleaning
costs_df <- dplyr::bind_rows(list(costs.total, costs.interviews, costs.applications, costs.virt.int, costs.other))
costs_df$cost <- plyr::mapvalues(x = costs_df$cost, from = c("Total.Costs.Centered", "Interview.Cost.Centered", "Application.Fees.Centered", "Virtual.Interview.Cost.Centered", "Other.Costs.Centered"), to = c("Total Costs", "Interview Costs", "Application Fees", "Virtual Interview Costs", "Other Costs"))
costs_df$cost <- factor(x = costs_df$cost, levels = c("Application Fees", "Interview Costs", "Virtual Interview Costs", "Other Costs", "Total Costs"))
costs_df$p_value <- signif(x = costs_df$p_value, digits = 2)

# Plotting a forest plot
forest_plot <- costs_df %>% 
  ggplot(aes(x = OR, xmin = conf.low, xmax = conf.high, y = reorder(Row.names, OR), color = likelihood)) + 
  geom_point() + 
  geom_errorbarh(height = 0.2) + 
  geom_text(aes(label = p_value, x = 2.5), hjust = 0, size = 3) + 
  facet_wrap(~cost, ncol = 5) +
  geom_vline(aes(xintercept = 1), color = "black", linetype = "dashed") + 
  scale_x_continuous(n.breaks = 8, limits = c(0, 4)) +
  scale_color_manual(values = c("#eb2323", "#525252", "#2e66ff")) +
  labs(x = "Odds Ratio [95% CI]", y = "Predictors", title = "Application and Interview Costs", color = "Odds") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 12))
print(forest_plot)

# Saving the plot
#ggsave(plot = forest_plot, filename = "figures/cost_analysis.png", width = 4000, height = 2300, dpi = 300, units = "px")
```



## 7.2 Cost of applying over time (virtual vs non-virtual due to COVID)

```{r}

```







## 3.9 School rankings

```{r}
# Importing doximity school rankings
dox <- read_xlsx(path = "tables/doximity_rankings.xlsx")
dox$program_specialty <- paste0(dox$program, "_", dox$specialty)  #used for merging in the next step

# Selecting columns and splitting by sort by rankings
dox <- dox[ , c("location", "program_size", "rank", "sort_by", "program_specialty")]
dox_reputation <- dox %>% dplyr::filter(sort_by == "reputation")
dox_research <- dox %>% dplyr::filter(sort_by == "research-output")
```

```{r}
# Merging programs applied to with selected applicant-level data
#cols_to_merge <- c("STAR.ID", "Specialty", "degrees")
#df_merge <- df_clean[, cols_to_merge]
#programs.dox <- merge(programs, df_merge, by = "STAR.ID", all.x = T)
#programs.dox$program_specialty <- paste0(programs.dox$Program.Institution, "_", programs.dox$Specialty)

programs.dox <- read.csv(file = "tables/STAR_Programs_2017_2023_final_matched.csv")
programs.dox$program_specialty <- paste0(programs.dox$Program.Institution.Dox, "_", programs.dox$Specialty)

# Merging doximity rankings by reputation
programs.dox.reputation <- merge(programs.dox, dox_reputation, by = "program_specialty", all.x = T)

# Merging doximity rankings by research output
programs.dox.research <- merge(programs.dox, dox_research, by = "program_specialty", all.x = T)
```

```{r}
# Summarizing reputation stats
rep.dox <- programs.dox.reputation %>% dplyr::group_by(STAR.ID) %>% 
  dplyr::summarise(
    specialty = unique(Specialty),
    degree = unique(degrees),
    application_count = n(),
    interviews_yes = sum(Interview.Offer == "Y"),
    matched = sum(Matched == "Y"), 
    geographic_connection_yes = sum(Geographic.Connection == "Y"), 
    geo_preference_eras_yes = sum(Geographic.Preference.ERAS.Supp.App == "Y"),
    away_rotation_yes = sum(Away.Rotation == "Y"),
    signaled_program_yes = sum(Signaled.Program == "Y"),
    program_size_mean = mean(program_size, na.rm = T),
    reputation_rank_mean = mean(rank, na.rm = T)
  )

# Summarizing research output stats
research.dox <- programs.dox.research %>% dplyr::group_by(STAR.ID) %>% 
  dplyr::summarise(
    specialty = unique(Specialty),
    degree = unique(degrees),
    application_count = n(),
    interviews_yes = sum(Interview.Offer == "Y"),
    matched = sum(Matched == "Y"), 
    geographic_connection_yes = sum(Geographic.Connection == "Y"), 
    geo_preference_eras_yes = sum(Geographic.Preference.ERAS.Supp.App == "Y"),
    away_rotation_yes = sum(Away.Rotation == "Y"),
    signaled_program_yes = sum(Signaled.Program == "Y"),
    program_size_mean = mean(program_size, na.rm = T),
    research_rank_mean = mean(rank, na.rm = T)
  )

# Counts for non-NA columns
non_na_lengths <- apply(research.dox, 2, function(x) length(na.omit(x)))
non_na_lengths
```

```{r}
# Stats for program size
rep.stats <- rep.dox %>% dplyr::filter(degree %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc"))
print(kruskal.test(program_size_mean ~ degree, data = rep.stats))
print(pairwise.wilcox.test(rep.stats$program_size_mean, rep.stats$degree, p.adjust.method = "fdr"))

# Stats for reputation
rep.stats <- rep.dox %>% dplyr::filter(degree %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc"))
print(kruskal.test(reputation_rank_mean ~ degree, data = rep.stats))
print(pairwise.wilcox.test(rep.stats$reputation_rank_mean, rep.stats$degree, p.adjust.method = "fdr"))

# Stats for research output
research.stats <- research.dox %>% dplyr::filter(degree %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc"))
print(kruskal.test(research_rank_mean ~ degree, data = research.stats))
print(pairwise.wilcox.test(research.stats$research_rank_mean, research.stats$degree, p.adjust.method = "fdr"))
```

```{r}
# Plotting by program size
program_size_plot <- rep.dox %>% dplyr::filter(degree %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
  ggplot(aes(x = degree, y = program_size_mean, fill = degree)) + 
  geom_boxplot(outliers = F) + 
  labs(x = "Degree", y = "Program Size", fill = "Degree", title = "Residency Program Size") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none")

# Plotting by reputation
reputation_plot <- rep.dox %>% dplyr::filter(degree %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
  ggplot(aes(x = degree, y = reputation_rank_mean, fill = degree)) + 
  geom_boxplot(outliers = F) + 
  labs(x = "Degree", y = "School Rank (Reputation)", fill = "Degree", title = "School Rank by Reputation") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none")

# Plotting by research output
research_plot <- research.dox %>% dplyr::filter(degree %in% c("MD", "MD-PhD", "MD-MPH", "MD-MSc")) %>% 
  ggplot(aes(x = degree, y = research_rank_mean, fill = degree)) + 
  geom_boxplot(outliers = F) + 
  labs(x = "Degree", y = "School Rank (Research Output)", fill = "Degree", title = "School Rank by Research Output") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none")

# Patchwork to merge the plots
school_ranks_plot <- program_size_plot | reputation_plot | research_plot
print(school_ranks_plot)

# Saving the plot
#ggsave(plot = school_ranks_plot, filename = "figures/school_rankings.png", width = 4000, height = 1500, dpi = 300, units = "px")
```

```{r}
# Are MD/PhD students matching to higher ranking residency programs?
rep.dox.matched <- programs.dox.reputation %>% dplyr::filter(Matched == "Y")
research.dox.matched <- programs.dox.research %>% dplyr::filter(Matched == "Y")

rep.df <- merge(rep.dox.matched, rep.dox[ , c("STAR.ID", "reputation_rank_mean")], by = "STAR.ID", all.x = T)
research.df <- merge(research.dox.matched, research.dox[ , c("STAR.ID", "research_rank_mean")], by = "STAR.ID", all.x = T)
```

```{r}
# Plotting by reputation for students that matched
reputation_plot <- rep.df %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")) %>% 
  tidyr::pivot_longer(cols = c("rank", "reputation_rank_mean"), names_to = "apply_match", values_to = "ranks") %>% 
  ggplot(aes(x = degrees, y = ranks, fill = apply_match)) + 
  geom_boxplot(outliers = F) + 
  labs(x = "Degree", y = "School Rank (Reputation)", fill = "Degree", title = "School Rank by Reputation") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")

# Plotting by research output for students that matched
research_plot <- research.df %>% dplyr::filter(degrees %in% c("MD", "MD-PhD", "MD-MPH", "MD-MBA", "MD-MSc")) %>% 
  tidyr::pivot_longer(cols = c("rank", "research_rank_mean"), names_to = "apply_match", values_to = "ranks") %>% 
  ggplot(aes(x = degrees, y = ranks, fill = apply_match)) + 
  geom_boxplot(outliers = F) + 
  labs(x = "Degree", y = "School Rank (Research Output)", fill = "Degree", title = "School Rank by Research Output") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")

# Combining plots
rep_research_plot <- reputation_plot | research_plot
print(rep_research_plot)
```



```{r}
# Exporting a csv for AI to match residency program names
dox <- read_xlsx(path = "tables/doximity_rankings.xlsx")
dox$program_specialty <- paste0(dox$program, "_", dox$specialty)  #used for merging in the next step
programs_dox <- unique(dox$program_specialty)
programs_star <- unique(programs.dox$program_specialty)

star_programs <- data.frame(star_programs = programs_star)
star_programs <- star_programs %>% tidyr::separate(col = "star_programs", into = c("program", "specialty"), sep = "_", remove = F)

unmatched_programs <- programs_star[!programs_star %in% programs_dox]
unmatched_programs <- data.frame(unmatched_programs = unmatched_programs)
unmatched_programs <- unmatched_programs %>% tidyr::separate(col = "unmatched_programs", into = c("program", "specialty"), sep = "_", remove = F)
unmatched_programs <- unmatched_programs %>% dplyr::arrange(specialty, program)

# Exporting to csv
#write_xlsx(x = df_programs, path = "tables/doximity_texasSTAR_unique_programs.xlsx")
#write.csv(x = star_programs, file = "tables/texasSTAR_unique_programs.csv", row.names = F)
#write.csv(x = unmatched_programs, file = "tables/unmatched_unique_programs.csv", row.names = F)
```
































































